### 2012-05-01 inst/examples/Sethi.Rmd
avoid repeat citation

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````
